### 2023-04-12 main.tex
i
pulizia

    \sum_{a=2}^{N}\alpha_{a}^{x}\left(E_{1a}^{x}+E_{11}^{x}-\sum_{c=2}^{N}E_{c1}^{x}+E_{ca}^{x}-E_{11}^{x}+\sum_{c=2}^{N}E_{c1}^{x}\right)+\alpha_{1}^{x}\sum_{b=2}^{N}\left(E_{b1}^{x}-E_{bb}^{x}-E_{b1}^{x}\right)
    \\&+\sum_{a=2}^{N}\sum_{b=2}^{N}\alpha_{a}^{x}\left(E_{ba}^{x}+E_{b1}^{x}-E_{bb}^{x}-E_{b1}^{x}\right)

@@

    % \exp{(-E^{x})}\sum_{a=2}^{N}\alpha_{a}^{x}\left(E_{1a}^{x}-E_{11}^{x}\right)\exp{(E^{x})}
     %+ \exp{(-E^{x})}\sum_{a=1}^{N}\sum_{b=2}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}-E_{bb}^{x}\right)\exp{(E^{x})}
     %\\=&
    % \sum_{a=2}^{N}\alpha_{a}^{x}\left(E_{1a}+E_{11}^{x}-\sum_{a=2}^{N}(E_{aa}^{x}+E_{a1}^{x})-E_{11}^{x}+\sum_{a=2}^{N}E_{a1}^{x}\right)+\sum_{a=1}^{N}\sum_{b =2}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}+E_{b 1}^{x}-E_{bb}^{x}-E_{b 1}^{x}\right)
    % \\=&
%\sum_{a=2}^{N}\alpha_{a}^{x}E_{1a}^{x}-\sum_{a=1}^{N}\alpha_{a}^{x}\sum_{b=2}^{N}E_{bb}^{x}
%=
  %   \sum_{a=2}^{N}\left(\alpha_{a}^{x}E_{1a}^{x}-\sum_{i=1}^{N}\alpha_{i}^{x}E_{aa}^{x}\right)
%=
%\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{a=2}^{N}\left(\frac{\alpha_{a}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}E_{1a}^{x}-E_{aa}^{x}\right)
%\\=&
%\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{a=2}^{N}\left(\rho_{a}^{x}E_{1a}^{x}-E_{aa}^{x}\right)

@@

&\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{a}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|\frac{\alpha_{a}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}E_{1a}^{x}

@@

In this section we specialize the multi-species stirring process to the geometry of the one dimensional chain with sites $\{1,\ldots,L\}$ where two reservoirs act at the boundary sites $1$ and $L$. These boundaries, exchanging particle with the external environment, by putting the chain out of equilibrium. The Hamiltonian that we consider here is obtained by \eqref{OriginalHamiltonian} assuming that the conductances are

@@

{\color{red} We will denote the element of the representation of the Lie algebra by lowercase letters, i.e. $e_{ab}$, since we are in the lowest spin case (the fundamental representation of algebra).} \\

@@

Under these assumption the Hamiltonian is integrable. \\

@@

 the master equation

@@

where $\mathcal{S}_{1}$ makes $H^{'}$ with both diagonal boundaries and $\mathcal{S}_{2}$ makes $H^{''}$ with left triangular boundary and right diagonal one. Thanks to these transformations the commutators \eqref{bulk} and the action on the boundary vectors \eqref{rightBoundary}, \eqref{leftBoundary} of the operators $(X_{a})_{a\in\{1,\ldots,N\}}$ of the MPA become simple, therefore, the steady state $|\Psi\rangle$ of $H^{''}$ will be written explicitly. Then, reversing the transformations we will retrieve $|\Psi^{''}\rangle$.\\

@@

 S_{1}:=\exp{\left(\sum_{a=2}^{N}e_{a1}\right)}=\mathbbm{1}+\sum_{a=2}^{N}e_{1a}

@@

The boundary Hamiltonians$B_{1}^{'}$ and $B_{L}^{'}$ are $\widetilde{H}_{0}$ and $\widetilde{H}_{L+1}$ without the extra-site bosonic creation operators $(a^{\dagger})_{a}^{0}$ and $(a^{\dagger})_{a}^{L+1}$, i.e.

@@

The steady state $|\Psi^{'}\rangle$ of $H^{'}$ fulfils the equations

@@

Using $\mathcal{S}$ we introduce 

@@

We state the following result. The steady state of the Hamiltonian $H^{''}$ is given by 

@@

|V \rangle$ and the normalization $Z_{L}$. We use the new commutations relations \eqref{commutationsBula},\eqref{commLEFT} and \eqref{commRIGHT}.\\
We have

@@

	\lambda_{a}\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{1}^{\ell-1}+\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{1}^{b-1}

@@

Therefore, multiplying by the boundary vectors we have 

@@

	W|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}

@@

Moreover, we have 

@@

			\Psi^{'}(\bm{s})=\sum_{x=1}^{L}\sum_{c_{x}=0}^{1-\delta_{s_{x},1}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{s_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{y}\right)\right)^{c_{l}}\beta_{s_{y}}^{(1-c_{y})(1-\delta_{s_{y},1})}

@@

Therefore, we have that 
\begin{equation}\label{ABS_intermediate}
	\begin{split}
		\Psi^{'}(\mathbf{s})&=(\mathcal{S}_{2}^{-1})_{\bm{s}}|\Psi^{''}\rangle\\&= \Psi^{''}(\mathbf{s})+\sum_{q_{1}= 1}^{L}(1-\delta_{s_{q_{1}},1})\Psi^{''}(s_{1},\ldots,\overbrace{1}^{s_{q_{1}}},\ldots,s_{L})\beta_{s_{q_{1}}}\\&+
		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})\Psi^{''}(s_{1},\ldots,\overbrace{1}^{s_{q_{1}}},\ldots,\overbrace{1}^{s_{q_{2}}},\ldots,s_{L})\beta_{a_{1}}\beta_{a_{2}}\\&+\ldots+\Psi^{''}(1,\ldots,1)\left(\prod_{x=1}^{L}(1-\delta_{s_{x},1})\right)\prod_{x=1}^{L}\left(\beta_{s_{x}}\right)^{1-\delta_{s_{x},1}}
	\end{split}
\end{equation}
For a fixed configuration $\bm{s}=(s_{1},\ldots,s_{N})$, using equation \eqref{ResulsBasis} and observing that 
\begin{equation}
  \left(1+\sum_{j=y}^{L}\delta_{s_{j},1}\right) =\left(2+L-y-\sum_{j=y}^{L}(1-\delta_{s_{y},1})\right)
\end{equation}
we obtain 
    \begin{equation}
\Psi^{''}(\bm{s})=\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{s_{x},1})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{s_{y}}\left(2+L-y-\sum_{j=y}^{L}(1-\delta_{s_{y},1})\right)\right)^{1-\delta_{s_{y},1}}
\end{equation}
Introducing
\begin{equation}
	c_{y}=(1-\delta_{s_{y},1}) \qquad \forall y\in \{1,\ldots L\}
\end{equation}
and replacing $\Psi^{'}(\bm{s})$ compute above in \eqref{ABS_intermediate} we obtain

%Because of the exponent $(1-\delta_{s_{x},1})$, the element $\Psi^{''}(\bm{s})$ has, up the term $\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{s_{x},1})}{\Gamma(L+2)}$, a contribution of a factor $\lambda_{s_{x}}\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{s_{x},1})\right)$ if the site is non empty, and a contribution of a factor "$1$" if the site is empty, it is convenient to introduce the $c_{i}$ of defined in \eqref{CiEquation}. Then, equation  \eqref{ABS_intermediate} reads 
\begin{equation}\label{elementsABS}
	\begin{split}
		\Psi^{'}(\mathbf{s})=\sum_{c_{1}=0}^{1-\delta_{s_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{s_{L},1}}\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{s_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\left(\beta_{s_{y}}\right)^{(1-c_{y})(1-\delta_{s_{y},1})}
	\end{split}
\end{equation} 
%Indeed, when $c_{i}=0$ this formula replaces the contribution in the square brackets with a $\beta_{s_{x}}$. 
Finally, considering all possible occupancy $\bm{s}$, we obtain \eqref{ABS-vect}.
\begin{flushright}
    $\square$
\end{flushright}
\subsubsection{The steady state of $H$}\label{subsectionSSH}
The steady state $|\Psi\rangle$ of the Hamiltonian $H$ is given by 
\begin{equation}\label{steadyStateH}
    |\Psi\rangle=\sum_{s_{1},\ldots,s_{L}=1}^{N}\Psi(\bm{s})|\bm{s}\rangle
\end{equation}
where for every $(s_{1},\ldots,s_{L})=\bm{s}$
\begin{equation}\label{steadyStateH-coeff}
    \begin{split}
        \Psi(\bm{s})&=\sum_{x=1}^{L}\sum_{c_{x}=0}^{1-\delta_{s_{x},1}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{s_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{s_{y}}^{(1-c_{y})(1-\delta_{s_{y},1})}
        \\&+
        \sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right) 
        \sum_{r=1}^{b}\sum_{d_{q_{r}}=2}^{N}
\\&
\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{b}}^{L}\sum_{c_{x}=0}^{1-\delta_{s_{x},1}}\sum_{p=1}^{b}\sum_{c_{q_{p}}=0}^{1}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(2+L)}
  \prod_{y=1\,:\, y\neq q_{1},\ldots,q_{b}}^{L}\left(\lambda_{s_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}
 \\ &
 \beta_{s_{y}}^{(1-c_{y})(1-\delta_{s_{y},1})}
 \prod_{t=1}^{b}\lambda_{d_{q_{t}}}\left(2+L-q_{t}-\sum_{j=q_{t}}^{L}c_{j}\right)^{c_{q_{t}}}\beta_{d_{q_{t}}}^{(1-c_{q_{t}})}
    \end{split}
\end{equation}
\textbf{Remark}: we observe that if no holes are present in \eqref{steadyStateH-coeff}, i.e. if $s_{x}\neq 1$ $\forall x\in \{1,\ldots,L\}$, then the second addend vanishes and
\begin{equation}\label{LinkABS-corr}
\Psi(\bm{s})=\Psi^{'}(\bm{s})
\end{equation}
When the configuration has holes, the presence of the second addend is motivated by the dependence of the "empty" in a fixed site from all others types in the same site.

\paragraph{Proof of formula \eqref{steadyStateH}} As a consequence of \eqref{S1-Inverse}, we only need to show how the transformation $\mathcal{S}_{1}^{-1}$ acts on the vector $|\Psi^{'}\rangle$. The matrix $S_{2}^{-1}$, acting on a single site, is given by 
\begin{equation}\label{S1-L1}
	S_{1}^{-1}=\sum_{s_{1}=1}^{N}e_{s_{1}}^{s_{1}}+(-1)\delta_{s_{1},1}\sum_{d_{1}=2}^{N}e_{1}^{d_{1}}
\end{equation}
Using the notation introduced in \eqref{notation1} and \eqref{notation2} we have that 
\begin{equation}
	\begin{split}
		\mathcal{S}_{1}^{-1}=\left(S_{1}^{\otimes L}\right)^{-1}&=\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L}=1}^{N}\left\{e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}\right.
		\\&
		+\left.\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{r=1}^{b}\sum_{d_{q_{r}}=2}^{N}e_{\ldots,s_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,s_{x},\ldots,\,d_{q_{r}}\,,\ldots}\right\} 
	\end{split}
\end{equation}
where $e_{\ldots,s_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,s_{x},\ldots,\,d_{q_{r}}\,,\ldots}$ denotes the matrix $e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}$ where the subscripts $s_{q_{1}},\ldots,s_{q_{b}}$ have been replaced by "1" and the superscripts $s_{q_{1}},\ldots,s_{q_{b}}$ have been replaced by $d_{q_{1}},\ldots,d_{q_{b}}$. \\
This is proved by induction. Indeed, for $L=1$ it is trivially true, by \eqref{S1-L1}. We assume that it is true for arbitrary $L\in \mathbb{N}$ and we prove that it holds for $L+1$. 
\begin{align*}
\left(S_{1}^{\otimes L}\right)^{-1}\otimes S_{1}^{-1}&=
\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L}=1}^{N}\left\{e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}\right. \\&+\left. \sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{r=1}^{b}\sum_{d_{q_{r}}=2}^{N}e_{\ldots,s_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,s_{x},\ldots,\,d_{q_{r}}\,,\ldots}\right\}
\\&\otimes
\left\{ \sum_{s_{1}=1}^{N}e_{s_{L+1}}^{s_{L+1}}+(-1)\delta_{s_{L+1},1}\sum_{d_{L+1}=2}^{N}e_{1}^{d_{L+1}}\right\}
\\&=
\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L+1}=1}^{N}\left\{e_{s_{1},\ldots,s_{L+1}}^{s_{1},\ldots,s_{L+1}}\right. \\&+\left. \sum_{b=1}^{L+1}(-1)^{b}\sum_{q_{1}=1}^{L+1}\sum_{q_{2}=q_{1}+1}^{L+1}\ldots\sum_{q_{b}=q_{b-1}+1}^{L+1}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{r=1}^{b}\sum_{d_{q_{r}}=2}^{N}e_{\ldots,s_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,s_{x},\ldots,\,d_{q_{r}}\,,\ldots}\right\}
\end{align*}
\begin{comment}

@@

indeed, in coordinates $q_{r}$ with $r=1,\ldots b$ the species $1$ is replaced by all other possible species from $2$ to $N$.  Finally, considering all possible occupations $\bm{s}=(s_{1},\ldots,s_{L})$ we obtain \eqref{steadyStateH}. 

@@

In this section we write a formula for the stationary steady state correlations between $m$- points of the chain, each of them occupied by a non empty species, i.e. a species with label from $2$ to $N$. This is motivated by interest of understanding how actual particles of the chain are correlated among each others and because the holes depends on the occupation of all other species, as a consequence of the constraint $n_{0}^{x}=\nu-\sum_{a=2}^{N}n_{a}^{x}$ for arbitrary $x\in \{1,\ldots,L\}$. Consider $m\in \{1,\ldots,L\}$ points with coordinates given by $\bm{y}=(y_{1},\ldots,y_{m})$, such that $y_{i}<y_{i+1}$ $\forall i\in \{1,\ldots,m-1\}$. In each of these points there is a particle of species $s_{x}\in \{2,\ldots,N\}$. Then, with respect to the non-equilibrium stationary distribution, the correlations among these particles are given by

@@

			f(c_{1},\ldots,c_{m})\prod_{k=1}^{m}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(y_{k},c_{k},\ldots,c_{m})

@@

		f(c_{1},\ldots,c_{m})=\frac{\Gamma(L+2-\sum_{i=1}^{m}c_{i})}{\Gamma(L+2)}

>>>>

    \sum_{a=2}^{N}\alpha_{a}^{x}\left(E_{1a}^{x}+E_{11}^{x}-\sum_{c=2}^{N}(E_{c1}^{x})-\sum_{c=2}^{N}(E_{ca}^{x})-E_{11}^{x}+
    \sum_{c=2}^{N}(E_{c1}^{x})\right)\\&+\alpha_{1}^{x}\sum_{b=2}^{N}\left(E_{b1}^{x}-E_{bb}^{x}-E_{b1}^{x}\right)+\sum_{a=2}^{N}\sum_{b=2}^{N}\alpha_{a}^{x}\left(E_{ba}^{x}+E_{b1}^{x}-E_{bb}^{x}-E_{b1}^{x}\right)

@@

@@

&\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{a}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|\rho_{a}^{x}E_{1a}^{x}

@@

In this section we specialize the multi-species stirring process to the geometry of the one dimensional chain with sites $\{1,\ldots,L\}$ where two reservoirs act at the boundary sites $1$ and $L$. These boundaries, exchanging particle with the external environment, put the chain out of equilibrium. The Hamiltonian that we consider here is obtained by \eqref{OriginalHamiltonian} assuming that the conductances are

@@

{\color{red} We will denote the element of the representation of the Lie algebra by lowercase letters, i.e. $e_{ab}$, since we are in the the fundamental representation of the algebra.} \\

@@

Under these assumption the Hamiltonian is integrable (see \cite{vanicat2017exact}). \\

@@

 the Master equation

@@

where $\mathcal{S}_{1}$ makes $H^{'}$ with both diagonal boundaries and $\mathcal{S}_{2}$ makes $H^{''}$ with left triangular boundary and right diagonal one. Thanks to these transformations the commutators \eqref{bulk} and the action on the boundary vectors \eqref{rightBoundary}, \eqref{leftBoundary} of the operators $(X_{a})_{a\in\{1,\ldots,N\}}$ of the MPA become simpler, therefore, the steady state $|\Psi^{''}\rangle$ of $H^{''}$ will be written explicitly. Then, reversing the transformations we will retrieve $|\Psi\rangle$.\\

@@

 S_{1}:=\exp{\left(\sum_{a=2}^{N}e_{1a}\right)}=\mathbbm{1}+\sum_{a=2}^{N}e_{1a}

@@

The boundary Hamiltonians $B_{1}^{'}$ and $B_{L}^{'}$ are $\widetilde{H}_{0}$ and $\widetilde{H}_{L+1}$ without the extra-site bosonic creation operators $(a^{\dagger})_{a}^{0}$ and $(a^{\dagger})_{a}^{L+1}$, i.e.

@@

The steady state $|\Psi^{'}\rangle$ of $H^{'}$ fulfils the equation

@@

We introduce 

@@

We state the following result: the steady state of the Hamiltonian $H^{''}$ is given by 

@@

|V \rangle$ and the normalization $Z_{L}$. Using \eqref{commutationsBula} we have

@@

	\lambda_{a}\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{1}^{\ell-1}+\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{1}^{\ell -1}

@@

Multiplying by the boundary vectors we have 

@@

@@

Moreover, we write 

@@

			\Psi^{'}(\bm{s})=\sum_{x=1}^{L}\sum_{c_{x}=0}^{1-\delta_{s_{x},1}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{s_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{y}\right)\right)^{c_{y}}\beta_{s_{y}}^{(1-c_{y})(1-\delta_{s_{y},1})}

@@

Therefore, we have that 
\begin{equation}\label{ABS_intermediate}
	\begin{split}
		\Psi^{'}(\mathbf{s})&=(\mathcal{S}_{2}^{-1})_{\bm{s}}|\Psi^{''}\rangle\\&= \Psi^{''}(\mathbf{s})+\sum_{q_{1}= 1}^{L}(1-\delta_{s_{q_{1}},1})\Psi^{''}(s_{1},\ldots,\overbrace{1}^{s_{q_{1}}},\ldots,s_{L})\beta_{q_{1}}\\&+
		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})\Psi^{''}(s_{1},\ldots,\overbrace{1}^{q_{1}},\ldots,\overbrace{1}^{q_{2}},\ldots,s_{L})\beta_{a_{1}}\beta_{a_{2}}\\&+\ldots+\Psi^{''}(1,\ldots,1)\left(\prod_{x=1}^{L}(1-\delta_{s_{x},1})\right)\prod_{x=1}^{L}\left(\beta_{s_{x}}\right)^{1-\delta_{s_{x},1}}
	\end{split}
\end{equation}
For a fixed configuration $\bm{s}=(s_{1},\ldots,s_{N})$, using equation \eqref{ResulsBasis} and observing that 
\begin{equation}
  \left(1+\sum_{j=y}^{L}\delta_{s_{j},1}\right) =\left(2+L-y-\sum_{j=y}^{L}(1-\delta_{s_{y},1})\right)
\end{equation}
we obtain 
    \begin{equation}
\Psi^{''}(\bm{s})=\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{s_{x},1})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{s_{y}}\left(2+L-y-\sum_{j=y}^{L}(1-\delta_{s_{y},1})\right)\right)^{1-\delta_{s_{y},1}}
\end{equation}
Introducing
\begin{equation}
	c_{y}=(1-\delta_{s_{y},1}) \qquad \forall y\in \{1,\ldots L\}
\end{equation}
and replacing $\Psi^{'}(\bm{s})$ computed above in \eqref{ABS_intermediate} we obtain

%Because of the exponent $(1-\delta_{s_{x},1})$, the element $\Psi^{''}(\bm{s})$ has, up the term $\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{s_{x},1})}{\Gamma(L+2)}$, a contribution of a factor $\lambda_{s_{x}}\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{s_{x},1})\right)$ if the site is non empty, and a contribution of a factor "$1$" if the site is empty, it is convenient to introduce the $c_{i}$ of defined in \eqref{CiEquation}. Then, equation  \eqref{ABS_intermediate} reads 
\begin{equation}\label{elementsABS}
	\begin{split}
		\Psi^{'}(\mathbf{s})=\sum_{c_{1}=0}^{1-\delta_{s_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{s_{L},1}}\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{s_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\left(\beta_{s_{y}}\right)^{(1-c_{y})(1-\delta_{s_{y},1})}
	\end{split}
\end{equation} 
%Indeed, when $c_{i}=0$ this formula replaces the contribution in the square brackets with a $\beta_{s_{x}}$. 
Finally, considering all possible configurations $\bm{s}$, we obtain \eqref{ABS-vect}.
\begin{flushright}
    $\square$
\end{flushright}
\subsubsection{The steady state of $H$}\label{subsectionSSH}
The steady state $|\Psi\rangle$ of the Hamiltonian $H$ is given by 
\begin{equation}\label{steadyStateH}
    |\Psi\rangle=\sum_{s_{1},\ldots,s_{L}=1}^{N}\Psi(\bm{s})|\bm{s}\rangle
\end{equation}
where for every $(s_{1},\ldots,s_{L})=\bm{s}$
\begin{equation}\label{steadyStateH-coeff}
    \begin{split}
        \Psi(\bm{s})&=\sum_{x=1}^{L}\sum_{c_{x}=0}^{1-\delta_{s_{x},1}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{s_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{s_{y}}^{(1-c_{y})(1-\delta_{s_{y},1})}
        \\&+
        \sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right) 
        \sum_{r=1}^{b}\sum_{d_{q_{r}}=2}^{N}
\\&
\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{b}}^{L}\sum_{c_{x}=0}^{1-\delta_{s_{x},1}}\sum_{p=1}^{b}\sum_{c_{q_{p}}=0}^{1}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(2+L)}
  \prod_{y=1\,:\, y\neq q_{1},\ldots,q_{b}}^{L}\left(\lambda_{s_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}
 \\ &
 \beta_{s_{y}}^{(1-c_{y})(1-\delta_{s_{y},1})}
 \prod_{t=1}^{b}\lambda_{d_{q_{t}}}\left(2+L-q_{t}-\sum_{j=q_{t}}^{L}c_{j}\right)^{c_{q_{t}}}\beta_{d_{q_{t}}}^{(1-c_{q_{t}})}
    \end{split}
\end{equation}
\textbf{Remark}: we observe that if no holes are present in \eqref{steadyStateH-coeff}, i.e. if $s_{x}\neq 1$ $\forall x\in \{1,\ldots,L\}$, then the second addend vanishes and
\begin{equation}\label{LinkABS-corr}
\Psi(\bm{s})=\Psi^{'}(\bm{s})
\end{equation}
When the configuration has holes, the presence of the second addend is motivated by the dependence of the "empty" in a fixed site from all others types in the same site.

\paragraph{Proof of formula \eqref{steadyStateH}} As a consequence of \eqref{S1-Inverse}, we only need to show how the transformation $\mathcal{S}_{1}^{-1}$ acts on the vector $|\Psi^{'}\rangle$. The matrix $S_{1}^{-1}$, acting on a single site, is given by 
\begin{equation}\label{S1-L1}
	S_{1}^{-1}=\sum_{s_{1}=1}^{N}e_{s_{1}}^{s_{1}}+(-1)\delta_{s_{1},1}\sum_{d_{1}=2}^{N}e_{1}^{d_{1}}
\end{equation}
Using the notation introduced in \eqref{notation1} and \eqref{notation2} we have that 
\begin{equation}
	\begin{split}
		\mathcal{S}_{1}^{-1}=\left(S_{1}^{\otimes L}\right)^{-1}&=\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L}=1}^{N}\left\{e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}\right.
		\\&
		+\left.\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{r=1}^{b}\sum_{d_{q_{r}}=2}^{N}e_{\ldots,s_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,s_{x},\ldots,\,d_{q_{r}}\,,\ldots}\right\} 
	\end{split}
\end{equation}
where $e_{\ldots,s_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,s_{x},\ldots,\,d_{q_{r}}\,,\ldots}$ denotes the matrix $e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}$ where the subscripts $s_{q_{1}},\ldots,s_{q_{b}}$ have been replaced by "1" and the superscripts $s_{q_{1}},\ldots,s_{q_{b}}$ have been replaced by $d_{q_{1}},\ldots,d_{q_{b}}$. \\
This is proved by induction. Indeed, for $L=1$ it is trivially true, by \eqref{S1-L1}. We assume that it is true for arbitrary $L\in \mathbb{N}$ and we prove that it holds for $L+1$. 
\begin{align*}
\left(S_{1}^{\otimes L}\right)^{-1}\otimes S_{1}^{-1}&=
\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L}=1}^{N}\left\{e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}\right. \\&+\left. \sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{r=1}^{b}\sum_{d_{q_{r}}=2}^{N}e_{\ldots,s_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,s_{x},\ldots,\,d_{q_{r}}\,,\ldots}\right\}
\\&\otimes
\left\{ \sum_{s_{1}=1}^{N}e_{s_{L+1}}^{s_{L+1}}+(-1)\delta_{s_{L+1},1}\sum_{d_{L+1}=2}^{N}e_{1}^{d_{L+1}}\right\}
\\&=
\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L+1}=1}^{N}\left\{e_{s_{1},\ldots,s_{L+1}}^{s_{1},\ldots,s_{L+1}}\right. \\&+\left. \sum_{b=1}^{L+1}(-1)^{b}\sum_{q_{1}=1}^{L+1}\sum_{q_{2}=q_{1}+1}^{L+1}\ldots\sum_{q_{b}=q_{b-1}+1}^{L+1}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{r=1}^{b}\sum_{d_{q_{r}}=2}^{N}e_{\ldots,s_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,s_{x},\ldots,\,d_{q_{r}}\,,\ldots}\right\}
\end{align*}
\begin{comment}

@@

indeed, in each coordinate $q_{r}$ with $r=1,\ldots b$ the species $1$ is replaced by all other possible species from $2$ to $N$.  Finally, considering all possible configurations $\bm{s}=(s_{1},\ldots,s_{L})$ we obtain \eqref{steadyStateH}. 

@@

In this section we write a formula for the stationary steady state correlations between $m$- points of the chain, each of them occupied by a non empty species, i.e. a species with label from $2$ to $N$. This is motivated by interest of understanding how actual particles of the chain are correlated among each others and also because the holes depends on the occupation of all other species, as a consequence of the constraint $n_{1}^{x}=\nu-\sum_{a=2}^{N}n_{a}^{x}$ for arbitrary $x\in \{1,\ldots,L\}$. Consider $m\in \{1,\ldots,L\}$ points with coordinates given by $\bm{y}=(y_{1},\ldots,y_{m})$, such that $y_{i}<y_{i+1}$ $\forall i\in \{1,\ldots,m-1\}$. In each of these points there is a particle of species $s_{x}\in \{2,\ldots,N\}$. Then, with respect to the non-equilibrium stationary distribution, the correlations among these particles are given by

@@

			f(L,c_{1},\ldots,c_{m})\prod_{k=1}^{m}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},\ldots,c_{m})

@@

		f(L,c_{1},\ldots,c_{m})=\frac{\Gamma(L+2-\sum_{i=1}^{m}c_{i})}{\Gamma(L+2)}
